---
title: "Teaching Philosophy Statement"
subtitle: ""
author: "David Hall"
date: ""
output:
  tufte::tufte_handout:
    citation_package: natbib
    latex_engine: xelatex
  tufte::tufte_html: default
  tufte::tufte_book:
    citation_package: natbib
    latex_engine: xelatex
bibliography: skeleton.bib
link-citations: yes
---

```{r setup, include=FALSE}
library(tufte)
# invalidate cache when the tufte version changes
knitr::opts_chunk$set(tidy = FALSE, cache.extra = packageVersion('tufte'))
options(htmltools.dir.version = FALSE)
```

My own thoughts on teaching are largely irrelevant (in my opinion) from my CTFP proposal,^[CHM 135, *Experiment 1: the Chemistry of Air Quality*] as my role largely centered on developing suitable hypotheses for student queries and establishing the infrastructure needed to supply upwards of a thousand students with unique data sets. The actual questions which students answer for grades were finalized by Dr. D'eon in consultation with the other CHM 135 summer session faculty. 

Until now, I have never explicitly though about my 'teaching philosophy'. Rather, I have always taught others how I learn best. That is to say, give me the tools to figure it out and let me get to work. And the idea of 'tools' was my North star while I developped my CTFP. 

Many of my struggles in my academic career stem from not knowing *how* to do things. Being the first person in my family to attend university, and coming from a hole in the wall high-school of ~70 students total, I always wished the tools, the *how*, were explicitly taught and not muddied about in another experiment. It's difficult to extract the workflow of data analysis when you're worrying about cramming in a lab report in your already busy schedule. So when I was working on this CTFP I focused on the tools. 

the aim of the experiment first and foremost, in my mind, is to introduce data analysis workflows to students, and introduce them to some of the main tools they'll be using. They're should be a steady focus on numeracy and graphicacy, and all questions asked of students should be open-ended and answered with genuine feedback. ideally every student would get 100% on their marks because, aesthetic choices aside, every student should submit the exact same plots/charts and should be able to derive the appropriate conclusions from their work. 


```{r bib, include=FALSE}
# create a bib file for the R packages used in this document
knitr::write_bib(c('base', 'rmarkdown'), file = 'skeleton.bib')
```
